Taylor approximation - based methods for bias correction

### 2021-09-03 aprroximation_bias_correction.rmd
Autocommit

## Population averaging
pop_none <- genpred(simple_mod, "age", "wealthindex", pop=TRUE, bias.adjust="none", modelname="pop-none")
pop_delta <- genpred(simple_mod, "age", "wealthindex", pop=TRUE, bias.adjust="delta", modelname="pop-delta")

## Averaged // centered??
centered_none <- genpred(simple_mod, "age", "wealthindex", pop=FALSE, bias.adjust="none", modelname="centered-none")
centered_delta <- genpred(simple_mod, "age", "wealthindex", pop=FALSE, bias.adjust="delta", modelname="centered-delta")
centered_taylor <- genpred(simple_mod, "age", "wealthindex", pop=FALSE, bias.adjust="taylor", modelname="centered-taylor")

@@

```{r simple_preds}
p1 <- (ggplot(pop_none, aes(x=age, y=fit, colour=model))
	+ geom_hline(yintercept=true_prop, lty=2, colour="grey")
	+ geom_line()
	+ geom_line(data=pop_delta, aes(x=age, y=fit, colour=model))
	+ geom_line(data=centered_none, aes(x=age, y=fit, colour=model))
	+ geom_line(data=centered_delta, aes(x=age, y=fit, colour=model))
	+ geom_line(data=centered_taylor, aes(x=age, y=fit, colour=model))
	+ scale_colour_manual(values=c("blue", "red", "black", "orange", "purple"))
	+ theme(legend.position="right")
)
print(p1)
```

>>>>

### Population averaging
#pop_none <- genpred(simple_mod, "age", "wealthindex", pop=TRUE, bias.adjust="none", modelname="pop-none")
#pop_delta <- genpred(simple_mod, "age", "wealthindex", pop=TRUE, bias.adjust="delta", modelname="pop-delta")
#
### Averaged // centered??
#centered_none <- genpred(simple_mod, "age", "wealthindex", pop=FALSE, bias.adjust="none", modelname="centered-none")
#centered_delta <- genpred(simple_mod, "age", "wealthindex", pop=FALSE, bias.adjust="delta", modelname="centered-delta")
#centered_taylor <- genpred(simple_mod, "age", "wealthindex", pop=FALSE, bias.adjust="taylor", modelname="centered-taylor")
#
```

@@

```{r simple_preds, echo=FALSE}
#p1 <- (ggplot(pop_none, aes(x=age, y=fit, colour=model))
#	+ geom_hline(yintercept=true_prop, lty=2, colour="grey")
#	+ geom_line()
#	+ geom_line(data=pop_delta, aes(x=age, y=fit, colour=model))
#	+ geom_line(data=centered_none, aes(x=age, y=fit, colour=model))
#	+ geom_line(data=centered_delta, aes(x=age, y=fit, colour=model))
#	+ geom_line(data=centered_taylor, aes(x=age, y=fit, colour=model))
#	+ scale_colour_manual(values=c("blue", "red", "black", "orange", "purple"))
#	+ theme(legend.position="right")
#)
# print(p1)
```
